To understand if the solution works it will be subjected to a test with origin in the requirement specification \ref{sec:reqspec}. The requirements, which will be tested, are listed here:

\begin{enumerate}
	\item Detect position of table.
	\item Detect position of balls.
	\item Identify balls with high accuracy.
	\item Identification and position of balls should be obtained within 1 second.
	\item Work with mixed light conditions and not only those stated in WPAB rules\ref{sec:rules}.
\end{enumerate}

The tests for the first four requirements will be done individually with the different locations and lighting as described in section \ref{sec:testsetup}. The fifth requirement will be tested within the other requirements by altering the light.

\subsection{Test setup}
\label{sec:testsetup}
The test will be done in two different locations with different pool tables. First in the pool lab located in room A6-314 on Niels Jernes Vej 12 in Aalborg where image and video material for the solution to this project were made. The second location is the DE-Klub which is a student bar located in A4-101 at Frederik Bajers Vej 7 in Aalborg. The pool tables can be seen in figure \ref{fig:diffpool}.\\

The tests will be made in two light conditions: normal and mixed. These conditions can be seen in figure \ref{fig:difflightcon}. The reason for not doing it in dark conditions were because of the used webcams inability to regulate the exposure correctly.\\

\fixme{Indsæt billeder.}

\subsection{1) Detect position of table}

This was tested several times and if the position of the table is within the view of the camera the table will be found.\\

\subsection{2) Detect position of balls}



\subsection{3) Identify balls with high accuracy}



\subsection{4) Identification and position of balls should be obtained within 1 second}

Profile daz shit!
